Fourmile Calibrations and Output

### 2025-02-21 fourmile_output_dec2024.Rmd
minor
updates to KGE fig (need to fix legend & add boxplot)

# add all to the plot below
kge_all <- flow_kge_all %>%
  mutate(year = 'all years') %>%
  rename(model_run = name,
         kge = value)

@@

ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge_revise)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "mako", name = "KGE", direction = -1) +
  geom_text(aes(label = round(kge_revise, 2)), color = "grey", size = 2.5) +
  theme_bw(base_size=20) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

>>>>

# add all to the plot below
kge_all <- flow_kge_all %>%
  mutate(year = 'All') %>%
  rename(model_run = name,
         kge = value)

@@

flow_plot_updated <- flow_plot_updated %>% 
  mutate(source = case_when(
    grepl("grid", model_run) ~ "grid",
    grepl("statn", model_run) ~ "statn"),
    year_excluded = str_extract(model_run, "\\d{4}$")) %>%
  mutate(year_excluded = if_else(model_run %in% c('gridall',
                                                       'statnall'),
                                  'None', year_excluded))

ggplot(flow_plot_updated, aes(x = year_excluded, y = year, fill = kge_revise)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "mako", name = "KGE", direction = -1) +
  #geom_text(aes(label = round(kge_revise, 2)), color = "grey", size = 2.5) +
  geom_text(aes(label = sprintf("%.2f", kge_revise)), color = "grey", size = 2.5) +
  theme_bw(base_size=20) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year",
       x='Year Excluded') +
  facet_wrap(~source,
             scales = 'free_x',
             labeller = as_labeller(c("grid" = "Gridded", "statn" = "Station"))) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16),  # Correct way to adjust legend title text
    legend.key.width = unit(1, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black")
  )

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap.png',
       dpi=600,
       width = 10,
       height = 6)
